%----------------------------------------------------------------
\cvsection{Employment}

%----------------------------------------------------------------
\begin{cventries}
	\cventry
	{Web Developer , Data Science Beginner}
	{Freelance}
	{Auckland, \enskip New Zealand}
	{April 2018 - Present}
	{
		\begin{cvitems}
			\item {Online chat room build with Express.js, Node.js, jQuery, and socket.io.\href{https://github.com/ChenMu1/chatroom}{\enskip \color{deepblue}{Online chat room}}
			\item{A React-Redux powered single page admin dashboard. Used progressive web application pattern, highly optimized for React application. The example pages with a small amount of effort that can hook up back-end and be ready to roll in no time.\href{https://github.com/ChenMu1/amazing-react-app}{\enskip \color{deepblue}{ Admin Dashboard}} 
			\item{Self studying Python, R Language, Machine Learning, Data Visualization in spare time\quad  \href{https://www.kaggle.com/chenmu1/kernels}{\color{deepblue} {Kaggle} }
		}
	 }
		}
		\end{cvitems}
	}
\end{cventries}

%----------------------------------------------------------------
\begin{cventries}
	\cventry
	{Software Developer}
	{\href{http://www.aimyplus.com/about}{aimyPlus}}
	{Auckland, \enskip New Zealand}
	{March 2017 – March 2018}
	{
		\begin{cvitems}
			{I was able to use my skills to facilitate and help drive the rapid growth in FamBam project(a social media platform for after school care).}\\
			\item {Technology used: C\# / ASP.NET MVC / MVVM / RESTful APIs /MS SQL}
			\item {Created RESTful APIs with attribute routing in ASP.NET Web API that allows sophisticated and effective application integration for activity providers.}
			\item{Coworking with UX and UI designers. Designed and developed interactive user interface using HTML5/CSS3, JavaScript, jQuery, Bootstrap, Adobe XD CC.} \\ \\
			{As a result of my work on the FamBam project, I was recommended to another development team by the general manager to support their project leader to build a new platform Billion (Billion is a Learning management system).}\\ \\
			 {Technology used: C\# / ASP.NET MVC / MVVM / RESTful APIs /MS SQL}
			\item {Designed new CV management system by using C\# and ASP.NET MVC.}
			\item {Re-designed user interface and implemented new features by using HTML5/CSS3, JavaScript, jQuery, and Bootstrap.}
		\end{cvitems}
	}
\end{cventries}

%----------------------------------------------------------------